Constant-round Blind Classical Verification of Quantum Sampling

### 2020-09-04 preliminaries.tex
Fix some wording

It is less simple to state what it means for a $\QPIP_\tau$ protocol to solve a $\SampBQP$ instance.
We cannot hope for the protocol's output distribution to be close to the true distribution,
since a cheating prover can abort to force the verifier output $\bot$ with arbitrary probability.
The natural relaxation is to first condition on acceptance, then require the same of the output distribution.
We must also add that the acceptance probability is at least noticeable.
By combining these two conditions, we arrive at the following definition.

>>>>

It is less simple to state what it means for a $\QPIP_\tau$ protocol to solve a $\SampBQP$ instance.
We cannot hope for the protocol's output distribution to be close to the true distribution,
since a cheating prover can abort to force the verifier output $\bot$ with arbitrary probability.
On the other hand, we can ask that the output distribution to be close to the true one whenever the protocol does not abort.
